---
title: "drc_fitting"
author: "ross"
date: "12/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(drc)
library(quantreg)
library(mcr)
library(broom)
library(lubridate)
library(tidyverse)

# Create custom ggplot theme
theme_custom <- function() {
  theme_bw(base_size = 10, base_family = "Arial") %+replace%
    theme(
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      panel.background = element_blank(),
      panel.border = element_rect(color = "black", fill = NA),
      legend.background = element_rect(fill = NA, colour = NA),
      axis.title = element_text(size = 7),
      axis.text = element_text(size = 5)
    )
}

# # Labeller for treatments
# treatment_labeller <- function(variable, value){
#   return(list(
#   'Normal'="High light",
#   'lowLight'="Low light")[value])
# }
# 

# Function to pivot IPAM data to long form with column for AOI
ipam_convert <- function(data) {
  data %>% select_if(~ !any(is.na(.))) %>%
  pivot_longer(cols = starts_with("f") | starts_with("y")) %>%
  separate(name, into = c("var", "aoi"), sep = "(?<=[A-Za-z_])(?=[0-9])")
}
```

# CBASS experiment

### Import rack, temperature, and coral position information
```{r}
# Import coral collection data
corals <- read_csv("data/classic_cbass/collection_metadata.csv") %>%
  mutate(date = as_date(as.character(date_CBASS)))

# Import CBASS metadata (positions of corals on racks, and CBASS temperatures of each rack)
rack_pos <- read_csv("data/classic_cbass/CBASS_rack_position_map.csv") %>%
  mutate(date = as_date(as.character(date)))
rack_temp <- read_csv("data/classic_cbass/CBASS_rack_temp_map.csv") %>%
  mutate(date = as_date(as.character(date)))

md <- full_join(rack_temp, rack_pos)
md <- md %>%
  unite(rack, rack_no, rack_config, sep = "")

# Replace certain rack names for joining with PAM data
## There were two '53C' racks on 20221204
md <- md %>%
  mutate(rack = case_when(date == "2022-12-04" & rack == "53C" & temp == 31 ~ "53C_31blue",
                          TRUE ~ rack))

```

### Import I-PAM data
```{r}
# Import PAM data
# List PAM files from 2021-09-06
pamfiles <- list.files(path = "data/classic_cbass/IPAM_data/cbass", pattern = "*.csv", recursive = TRUE, full.names = TRUE)

# Import data from each file
pam1 <- pamfiles %>%
  map_dfr(read_delim, delim = ";", .id = "file_id") %>%
  janitor::clean_names() %>%
  mutate(file_id = basename(pamfiles[as.numeric(file_id)]),
         date = as_date(date, format = "%d.%m.%y"))

# # For files that have multiple sat pulses -- keep the last one only
# pam1 <- pam1 %>%
#   group_by(file_id, date) %>%
#   filter(no == max(no)) %>%
#   ungroup()

# For each source file, convert to long form data with F, FM, and YII for each AOI
pam1 <- pam1 %>%
  nest(-file_id, -date) %>%
  mutate(data2 = map(data, ipam_convert)) %>%
  unnest(data2) %>%
  group_by(file_id, date) %>%
  select(file_id, date, time, aoi, var, value)

pam1 <- pam1 %>%
  separate(file_id, into = c("rack", "junk"))
  

# Join PAM data with rack order information (which PAM file corresponds to which rack of corals)
pam <- pam1 %>%
  group_by(rack, date) %>%
  mutate(position = ceiling(as.numeric(aoi)/2)) %>%
  ungroup()

pam <- left_join(pam, md) %>% left_join(corals)
```

### Fit dose-response curves
```{r}
# Get Fv/Fm data and tidy
df <- pam %>%
  mutate(max_temp = as.numeric(temp)) %>%
  pivot_wider(names_from = var, values_from = value) %>%
  mutate(fvfmraw = y_ii_, fvfm = y_ii_) %>%
  select(date, tag_no, max_temp, f, fm, fvfmraw, fvfm)

# Define function to fit 3-parameter LL model to data and return NULL if fitting error
ll3 <- function(data) {
  drm(fvfm ~ max_temp, data = data, 
      fct = LL.3(names = c("hill", "max", "ED50")))}#,
      # upperl = c(50, 0.7, 40),
      # lowerl = c(20, 0.3, 30))}
tryll3 <- possibly(ll3, otherwise = NULL)

# Fit model to each coral, get parameters, fitted values, and residuals
initmods <- df %>%
  nest(data = c(date, max_temp, f, fm, fvfmraw, fvfm)) %>%
  # Fit the model to each coral
  mutate(ll3 = map(data, tryll3)) %>%
  # Get model parameters and fitted values/residuals
  mutate(pars = map(ll3, tidy),
         pred = map2(ll3, data, ~augment(.x, drop_na(.y, fvfm))))

# Extract ed50 parameter values from model fits
ed50 <- initmods %>% 
  select(tag_no, pars) %>%
  unnest(pars) %>%
  filter(term == "ED50")

hist(ed50$estimate, breaks = 30)

# Collect raw data, fitted values, and diagnostics
vals <- initmods %>%
  select(tag_no, pred) %>%
  unnest(pred) %>%
  full_join(ed50) %>%
  full_join(df) %>%
  rename(ed50 = estimate) %>%
  mutate(problem = "none")
```

### Filter outliers
```{r drc_diagnostics}
# # Identify problematic data points based on cook's distance and residuals
counts <- vals %>%
  mutate(geno = tag_no) %>%
  group_by(geno) %>%
  summarise(n = sum(!is.na(fvfm)))
dff <- vals %>%
  mutate(geno = tag_no) %>%
  left_join(counts) %>%
  group_by(geno) %>%
  mutate(cooksd.thresh = 4/n) %>%   # Calculate cook's distance threshold as 4/n
  mutate(max_to_remove = floor(n * 0.2)) %>%
  ungroup() %>%
  mutate(problem = case_when(.cooksd > cooksd.thresh ~ "high cook's distance",
                             TRUE ~ "none")) %>%
  group_by(geno, outlier = problem %in% c("high cook's distance", "high residual")) %>%
  mutate(n.outliers = n(),
         rank.out = order(.cooksd, decreasing = TRUE)) %>%
  ungroup() %>%
  mutate(fvfm = case_when(outlier & rank.out <= max_to_remove ~ .fitted,
                          TRUE ~ fvfm))

# Refit models without problematic points
fmods <- dff %>%
  select(geno, max_temp, f, fm, fvfmraw, problem, fvfm) %>%
  nest(data = c(max_temp, f, fm, fvfmraw, fvfm, problem)) %>%
  # Fit the model to each coral
  mutate(ll3 = map(data, tryll3)) %>%
  # Get model parameters and fitted values/residuals
  mutate(pars = map(ll3, tidy),
         pred = map2(ll3, data, ~augment(.x, drop_na(.y, fvfm))))

# Extract ed50 parameter values from model fits
fed50 <- fmods %>%
  select(geno, pars) %>%
  unnest(pars) %>%
  filter(term == "ED50")

# Collect raw data, fitted values, and ed50 estimates
fvals <- fmods %>%
  select(geno, pred) %>%
  unnest(pred) %>%
  full_join(fed50) %>%
  full_join(select(dff, geno, max_temp, f, fm, fvfmraw, problem, fvfm)) %>%
  rename(ed50 = estimate)
```

### Plot dose response curves for each genotype
```{r plot, fig.width = 10, fig.height = 10}
ed50 <- ed50 %>%
  mutate(geno = factor(tag_no))


vals <- vals %>%
  mutate(geno = fct_reorder(factor(tag_no), ed50, .fun = mean))
fvals <- fvals %>%
  mutate(geno = fct_reorder(factor(geno), ed50, .fun = mean))

ggplot(vals, aes(x = max_temp, y = fvfm)) +
  geom_point() +
  geom_line(aes(y = .fitted)) +
  geom_vline(aes(xintercept = estimate), data = ed50, lty = 2) +
  geom_text(aes(x = estimate, y = 0.05, label = round(estimate, 2)), data = ed50,
            size = 2, nudge_x = -1.5) +
  facet_wrap(~geno)
```

### Write ED50s to file
```{r}
fed50 %>%
  mutate(tag_no = factor(geno)) %>%
  full_join(ed50, by = c("tag_no", "term", "curve")) %>%
  select(geno, ed50 = estimate.y, std.error = std.error.y,
         ed50.f = estimate.x, std.error.f = std.error.x) %>%
  write_csv(path = "data/classic_cbass/processed/ed50.csv")
```

#---------

# Classic experiment

### Import rack, temperature, and coral position information
```{r}
# Import slowburn metadata (positions of corals on racks, and treatments)
rack_pos <- read_csv("data/classic_cbass/CLASSIC_rack_position_map.csv") %>%
  mutate(date = as_date(as.character(date)))

md <- rack_pos %>%
  filter(time == "evening")
```

### Import I-PAM data
```{r}
# Import PAM data
# List PAM files from 2021-09-06
pamfiles <- list.files(path = "data/classic_cbass/IPAM_data/classic", pattern = "*.csv", recursive = TRUE, full.names = TRUE)

slowburnpamfiles <- pamfiles[grepl("Slow", pamfiles)]

# Import data from each file
pam1 <- slowburnpamfiles %>%
  map_dfr(read_delim, delim = ";", .id = "file_id") %>%
  janitor::clean_names() %>%
  mutate(file_id = basename(slowburnpamfiles[as.numeric(file_id)]),
         date = as_date(date, format = "%d.%m.%y"))

# # For files that have multiple sat pulses -- keep the last one only
pam1 <- pam1 %>%
  group_by(file_id, date) %>%
  filter(no == max(no)) %>%
  ungroup()

# For each source file, convert to long form data with F, FM, and YII for each AOI
pam1 <- pam1 %>%
  nest(-file_id, -date) %>%
  mutate(data2 = map(data, ipam_convert)) %>%
  unnest(data2) %>%
  group_by(file_id, date) %>%
  select(file_id, date, time, aoi, var, value)

pam1 <- pam1 %>%
  separate(file_id, into = c("rack_no", "junk")) %>%
  mutate(rack_no = as.numeric(rack_no))
  

# Join PAM data with rack order information (which PAM file corresponds to which rack of corals)
pam <- pam1 %>%
  group_by(rack_no, date) %>%
  mutate(position = ceiling(as.numeric(aoi)/2)) %>%
  ungroup()

pam <- left_join(pam, md, by = c("date", "rack_no", "position"))
```


```{r}
pam <- pam %>%
  separate(frag_id, into = c("genotype", "frag"))

res <- pam %>%
  filter(date == "2022-12-13", var == "y_ii_") %>%
  group_by(genotype, treatment) %>%
  summarize(mean = mean(value), sd = sd(value)) %>%
  ungroup() %>%
  mutate(genotype = fct_reorder(factor(genotype), mean))


res %>%
  ggplot(aes(x = genotype, y = mean, color = treatment)) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd)) +
  geom_point()

sbres <- res %>% 
  select(genotype, treatment, mean) %>%
  pivot_wider(names_from = treatment, values_from = mean) %>%
  mutate(decline = high - ambient)
```

# Compare CBASS vs. Classic
```{r}
both <- sbres %>%
  left_join(mutate(fed50, genotype = factor(geno)))

library(ggpubr)
ggplot(both, aes(x = estimate, y = decline)) +
  geom_point() +
  geom_smooth(method = "lm") +
  geom_label(aes(label = genotype)) +
  stat_cor(method = "pearson", label.y = -0) + 
  labs(x = "Heat tolerance measured by CBASS (ED50)", y = "Heat tolerance measured in\nclassic bleaching experiment (Drop in Fv/Fm)")

mod <- lm(decline ~ estimate, data = both)
anova(mod)

```

# Plot temperature profiles

### CBASS experiment profiles
```{r}
# Read in CBASS temperature logs and filter for just December 4th run
cbasslogs <- list("data/classic_cbass/temperature_logs/LOG_28.5_35_34_37_right.TXT",
                  "data/classic_cbass/temperature_logs/LOG_31_38_33_36_left.TXT")

cbasstemps <- map_dfr(cbasslogs, read_csv) %>%
  # Remove internal header rows
  filter(PrintDate != "PrintDate") %>%
  # Format date and time
  mutate(date = as_date(Date, format = "%Y_%m_%d")) %>%
  unite(time, Th, Tm, Ts, sep = ":") %>%
  unite(dttm, date, time) %>%
  mutate(dttm = ymd_hms(dttm)) %>%
  # Filter to just December 4th run
  filter(dttm >= as_datetime("2022-12-04 11:20:00") & dttm <= as_datetime("2022-12-04 20:00:00")) %>%
  select(dttm, ShortUniqueID, T1SP, TempT1, T2SP, TempT2, T3SP, TempT3, T4SP, TempT4) %>%
  # Pivot to long format
  pivot_longer(starts_with("T"), names_to = "key", values_to = "temp") %>%
  # Remove rows where temp sensors gave error codes
  filter(temp > 0, temp < 50) %>%
  # Parse tanks, setpoints, and actual temps
  mutate(probe = str_extract(key, "T[0-9]"),
         key = case_when(grepl("SP", key) ~ str_sub(key, 3, 4),
                         TRUE ~ str_sub(key, 1, 4)),
         key = tolower(key)) %>%
  # Filter to only get one temperature reading per second by averaging
  group_by(dttm, ShortUniqueID, probe, key) %>%
  summarize(temp = mean(as.numeric(temp), na.rm = TRUE)) %>%
  ungroup() %>%
  # Create columns for set point and actual temperature
  pivot_wider(names_from = key, values_from = temp) %>%
  # Tidy column types
  mutate(probe = factor(probe)) %>%
  # Add maximum setpoint temperature as max_temp column
  group_by(ShortUniqueID, probe) %>%
  mutate(max_temp = factor(max(sp, na.rm = TRUE))) %>%
  ungroup()

cbasstempsfig <- ggplot(cbasstemps, aes(x = dttm, y = temp, color = max_temp)) +
  geom_line() +
  theme_custom() +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(26.9, 38.2), breaks = seq(27, 38, 1)) +
  labs(x = "", y = "Temperature (°C)"); cbasstempsfig

ggsave(cbasstempsfig, filename = "output/cbass_temps.png", width = 60, height = 80, units = "mm")
  

```


### Classic experiment profiles
```{r}
temps <- read_csv("data/classic_cbass/temperature_logs/LOG_CLASSIC.TXT") %>%
    # Remove internal header rows
    filter(PrintDate != "PrintDate") %>%
    # Format date and time
    mutate(date = as_date(Date, format = "%Y_%m_%d")) %>%
    unite(time, Th, Tm, Ts, sep = ":") %>%
    unite(dttm, date, time) %>%
    mutate(dttm = ymd_hms(dttm)) %>%
    select(dttm, T1SP, TempT1, T2SP, TempT2, T3SP, TempT3, T4SP, TempT4) %>%
    # Pivot to long format
    pivot_longer(starts_with("T"), names_to = "key", values_to = "temp") %>%
    # Remove rows where temp sensors gave error codes
    filter(temp > 0, temp < 50) %>%
    # Parse tanks, setpoints, and actual temps
    mutate(probe = str_extract(key, "T[0-9]"),
           key = case_when(grepl("SP", key) ~ str_sub(key, 3, 4),
                           TRUE ~ str_sub(key, 1, 4)),
           key = tolower(key)) %>%
    # Filter to only get one temperature reading per second by averaging
    group_by(dttm, probe, key) %>%
    summarize(temp = mean(as.numeric(temp), na.rm = TRUE)) %>%
    ungroup() %>%
    # Create columns for set point and actual temperature
    pivot_wider(names_from = key, values_from = temp) %>%
    # Tidy column types
    mutate(probe = factor(probe)) %>%
    # Add maximum setpoint temperature as max_temp column
    group_by(probe) %>%
    mutate(max_temp = max(sp, na.rm = TRUE)) %>%
    ungroup()
  

# Sort out which probes were in which tanks at which times from field notes
temps <- temps %>%
  drop_na(temp) %>%
  mutate(tank = case_when(
    (dttm > as_datetime("2022-12-06 09:36:00") & dttm < as_datetime("2022-12-06 14:25:00") & probe == "T2") ~ "T3",
    (dttm > as_datetime("2022-12-06 09:36:00") & dttm < as_datetime("2022-12-06 14:25:00") & probe == "T1") ~ "T2",
    (dttm > as_datetime("2022-12-06 14:25:00") & dttm < as_datetime("2022-12-07 08:20:00") & probe == "T2") ~ "NA",
    (dttm > as_datetime("2022-12-06 14:25:00") & dttm < as_datetime("2022-12-07 08:20:00") & probe == "T1") ~ "T2",
    (dttm > as_datetime("2022-12-06 09:36:00") & dttm < as_datetime("2022-12-07 08:20:00") & probe == "T4") ~ "NA",
    (dttm > as_datetime("2022-12-13 11:17:00") & probe == "T1") ~ "T2",
    (dttm > as_datetime("2022-12-13 11:15:00") & probe == "T2") ~ "T1",
    TRUE ~ as.character(probe))) %>%
  filter(tank != "NA")

# Filter out erroneous readings (probes removed from tank, or other obvious errors)
library(pracma)
t1 <- filter(temps, tank == "T1")
ggplot(t1, aes(x = dttm, y = temp)) + geom_line()
hamp1 <- hampel(t1$temp, 400, 2)
t1 <- t1 %>% mutate(out = row_number() %in% hamp1$ind)
ggplot(t1, aes(x = dttm, y = temp)) + geom_point(aes(color = out))

t2 <- filter(temps, tank == "T2")
ggplot(t2, aes(x = dttm, y = temp)) + geom_point()
hamp2 <- hampel(t2$temp, 200, 10)
t2 <- t2 %>% mutate(out = row_number() %in% hamp2$ind)
ggplot(t2, aes(x = dttm, y = temp)) + geom_point(aes(color = out))

t3 <- filter(temps, tank == "T3")
ggplot(t3, aes(x = dttm, y = temp)) + geom_point()
hamp3 <- hampel(t3$temp, 200, 10)
t3 <- t3 %>% mutate(out = row_number() %in% hamp3$ind)
ggplot(t3, aes(x = dttm, y = temp)) + geom_point(aes(color = out))

t4 <- filter(temps, tank == "T4")
ggplot(t4, aes(x = dttm, y = temp)) + geom_point()
hamp4 <- hampel(t4$temp, 500, 4)
t4 <- t4 %>% mutate(out = row_number() %in% hamp4$ind)
ggplot(t4, aes(x = dttm, y = temp)) + geom_point(aes(color = out))

# Replace outliers with imputed values
temps <- temps %>%
  arrange(tank, dttm) %>%
  mutate(hamp = c(hamp1$y, hamp2$y, hamp3$y, hamp4$y))

# Turn implicit missing values into explicit missing values so that lines are not drawn across gaps in data
temps <- temps %>% 
  select(dttm, tank, temp, hamp) %>%
  complete(dttm, tank)

# Plot classic temperatre profiles
classictemps <- ggplot(temps, aes(x = dttm, y = hamp, color = tank)) +
  geom_line(lwd = 0.5) +
  scale_x_datetime(breaks = "days", date_labels = "%b %d") +
  theme_custom() +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(26.9, 38.2), breaks = seq(27, 38, 1)) +
  labs(x = "", y = ""); classictemps

ggsave(classictemps, filename = "output/classic_temps.png", width = 100, height = 80, units = "mm")
```

### Combined profiles figure
```{r}
library(cowplot)
profiles <- plot_grid(cbasstempsfig, classictemps, nrow = 1, rel_widths = c(0.4, 0.6), labels = "auto")
ggsave(profiles, filename = "output/cbass_classic_profiles.png", width = 183, height = 80, units = "mm")
```

