---
title: "Reproducibility test"
author: "ross"
date: "8/25/2022"
output: html_document
---

```{r setup, include=FALSE}
options(rlib_downstream_check = FALSE)
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs_fxns}
library(drc)
library(quantreg)
library(mcr)
library(broom)
library(lubridate)
library(tidyverse)

# Create custom ggplot theme
theme_custom <- function() {
  theme_bw(base_size = 10, base_family = "Arial") %+replace%
    theme(
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank(), 
      panel.background = element_blank(),
      panel.border = element_rect(color = "black", fill = NA),
      legend.background = element_rect(fill = NA, colour = NA),
      axis.title = element_text(size = 7),
      axis.text = element_text(size = 5)
    )
}

# Function to pivot IPAM data to long form with column for AOI
ipam_convert <- function(data) {
  data %>% select_if(~ !any(is.na(.))) %>%
  pivot_longer(cols = starts_with("f") | starts_with("y")) %>%
  separate(name, into = c("var", "aoi"), sep = "(?<=[A-Za-z_])(?=[0-9])")
}
```

# Import data
```{r import_data}
# Import metadata: order in which racks PAMmed, and order of genets on racks
genetmd <- readxl::read_xlsx("data/reproducibility/genet_map.xlsx") %>%
  mutate(date = as_date(date), position = as.numeric(position))
pammd <- readxl::read_xlsx("data/reproducibility/pam_order.xlsx") %>%
  mutate(file_id = paste0(file_id, ".csv"),
         date = as_date(date), n_corals = as.numeric(n_corals))

# Import PAM data
# List PAM files from 2021-09-06 and 2021-09-08
pamfiles1 <- list.files(path = "data/reproducibility/PAM_data/20210906_1", pattern = "*.csv", full.names = T)
pamfiles2 <- list.files(path = "data/reproducibility/PAM_data/20210908_1", pattern = "*.csv", full.names = T)
pamfiles <- c(pamfiles2, pamfiles1)

# Import data from each file
pam1 <- pamfiles %>%
  map_dfr(read_delim, delim = ";", .id = "file_id") %>%
  janitor::clean_names() %>%
  mutate(file_id = basename(pamfiles[as.numeric(file_id)]),
         date = as_date(date, format = "%d.%m.%y"))

# For files that have multiple sat pulses -- keep the last one only
pam1 <- pam1 %>%
  group_by(file_id, date) %>%
  filter(no == max(no)) %>%
  ungroup()

# For each source file, convert to long form data with F, FM, and YII for each AOI
pam1 <- pam1 %>%
  nest(-file_id, -date) %>%
  mutate(data2 = map(data, ipam_convert)) %>%
  unnest(data2) %>%
  group_by(file_id, date) %>%
  select(file_id, date, time, aoi, var, value)

# Join PAM data with rack order information (which PAM file corresponds to which rack of corals)
pam <- full_join(pam1, pammd) %>%
  group_by(file_id, date) %>%
  mutate(position = case_when(max(aoi) > n_corals ~ ceiling(as.numeric(aoi)/2),
                              max(aoi) == n_corals ~ as.numeric(aoi)))

# Join PAM data with coral genet and temperature treatment information (which AOI corresponds to which coral)
pam <- genetmd %>%
  full_join(pam, by = c("date", "rack", "position"))

# how many fvfm meas per genet per temp?
pam %>%
  filter(var == "y_ii_") %>%
  count(genet, temp) %>%
  arrange(-n)
```

# Fit dose-response curves to estimate ED50s
```{r fit_drc}
# Get Fv/Fm data and tidy
df <- pam %>%
  mutate(max_temp = as.numeric(temp)) %>%
  pivot_wider(names_from = var, values_from = value) %>%
  mutate(fvfmraw = y_ii_, fvfm = y_ii_) %>%
  select(geno = genet, nursery, max_temp, f, fm, fvfmraw, fvfm)

# Define function to fit 3-parameter LL model to data and return NULL if fitting error
ll3 <- function(data) {
  drm(fvfm ~ max_temp, data = data, 
      fct = LL.3(names = c("hill", "max", "ED50")),
      upperl = c(50, 0.7, 40),
      lowerl = c(20, 0.3, 30))}
tryll3 <- possibly(ll3, otherwise = NULL)

# Fit model to each coral, get parameters, fitted values, and residuals
initmods <- df %>%
  nest(data = c(max_temp, f, fm, fvfmraw, fvfm)) %>%
  # Fit the model to each coral
  mutate(ll3 = map(data, tryll3)) %>%
  # Get model parameters and fitted values/residuals
  mutate(pars = map(ll3, tidy),
         pred = map2(ll3, data, ~augment(.x, drop_na(.y, fvfm))))

# Extract ed50 parameter values from model fits
ed50 <- initmods %>% 
  select(nursery, geno, pars) %>%
  unnest(pars) %>%
  filter(term == "ED50")

# Collect raw data, fitted values, and diagnostics
vals <- initmods %>%
  select(nursery, geno, pred) %>%
  unnest(pred) %>%
  full_join(ed50) %>%
  full_join(df) %>%
  rename(ed50 = estimate) %>%
  mutate(problem = "none")
```

```{r drc_diagnostics}
# # Identify problematic data points based on cook's distance and residuals
counts <- vals %>%
  group_by(nursery, geno) %>%
  summarise(n = sum(!is.na(fvfm)))
dff <- vals %>%
  left_join(counts) %>%
  group_by(nursery, geno) %>%
  mutate(cooksd.thresh = 4/n) %>%   # Calculate cook's distance threshold as 4/n
  mutate(max_to_remove = floor(n * 0.2)) %>%
  ungroup() %>%
  mutate(problem = case_when(.cooksd > cooksd.thresh & !max_temp %in% c(30, 38) ~ "high cook's distance", # don't allow 30 and 38 to be removed based on cooksd
                             TRUE ~ "none")) %>%
  group_by(nursery, geno, outlier = problem %in% c("high cook's distance", "high residual")) %>%
  mutate(n.outliers = n(),
         rank.out = order(.cooksd, decreasing = TRUE)) %>%
  ungroup() %>%
  mutate(fvfm = case_when(outlier & rank.out <= max_to_remove & !max_temp %in% c(30, 38) ~ NA_real_,
                          TRUE ~ fvfm))

# Refit models without problematic points
fmods <- dff %>%
  select(nursery, geno, max_temp, f, fm, fvfmraw, problem, fvfm) %>%
  nest(data = c(max_temp, f, fm, fvfmraw, fvfm, problem)) %>%
  # Fit the model to each coral
  mutate(ll3 = map(data, tryll3)) %>%
  # Get model parameters and fitted values/residuals
  mutate(pars = map(ll3, tidy),
         pred = map2(ll3, data, ~augment(.x, drop_na(.y, fvfm))))

# Extract ed50 parameter values from model fits
fed50 <- fmods %>%
  select(nursery, geno, pars) %>%
  unnest(pars) %>%
  filter(term == "ED50")

# Collect raw data, fitted values, and ed50 estimates
fvals <- fmods %>%
  select(nursery, geno, pred) %>%
  unnest(pred) %>%
  full_join(fed50) %>%
  full_join(select(dff, nursery, geno, max_temp, f, fm, fvfmraw, problem, fvfm)) %>%
  rename(ed50 = estimate)
```

# Plot dose response curves for each genotype
```{r plot, fig.width = 10, fig.height = 10}
# Plot fits
## Reorder genotypes by ED50 in decreasing order
fvals.ord <- fvals %>%
  mutate(geno = fct_reorder(factor(geno), ed50, .fun = mean, na.rm = TRUE, .desc = TRUE))
vals.ord <- vals %>%
  mutate(geno = factor(geno, levels = levels(fvals.ord$geno)))
ed50 <- ed50 %>% mutate(geno = factor(geno, levels = levels(fvals.ord$geno)))
fed50 <- fed50 %>% mutate(geno = factor(geno, levels = levels(fvals.ord$geno)))

ggplot(fvals.ord, aes(x = max_temp)) + 
    facet_wrap(~ geno) +
    geom_point(aes(y = fvfmraw, shape = is.na(fvfm)), size = 1) + 
    geom_line(data = drop_na(fvals.ord), aes(y = .fitted), lty = 1) + 
    geom_line(data = vals.ord, aes(y = .fitted), lty = 2) + 
    geom_vline(data = ed50, aes(xintercept = estimate), lwd = 0.25, lty = 2) +
    geom_vline(data = fed50, aes(xintercept = estimate), lwd = 0.25, lty = 1) +
    scale_shape_manual(values = c(1, 4)) +
    geom_text(data = fed50,
              aes(x = estimate, y = 0.05, label = round(estimate, 2)), 
              hjust = 1, nudge_x = -0.2, size = 2) +
    theme_classic() +
    theme(legend.position = "none")
```

# Compare ED50s measured in 2021 to ED50s measured in 2020
```{r}
# Import data from 2020
ed50_2020 <- read_csv("~/Projects/CBASS_FL_Acer/data/processed/ed50_values.csv") %>%
  mutate(nursery = case_when(nursery == "mote" ~ "mml", TRUE ~ nursery)) %>%
  select(nursery, geno, ed50_2020 = ed50, std.error_2020 = std.error)

# In 2020, some genotypes were run multiple times from the same nursery, indicated by (A), (B), (C), etc.
# Group these, and get the average ED50 for 2020 for each genotype from each nursery
ed50_2020 <- ed50_2020 %>%
  separate(geno, into = c("geno", "replicate"), sep = "\\(") %>%
  group_by(geno, nursery) %>%
  summarise(ed50_2020 = weighted.mean(ed50_2020, 1/std.error_2020^2), 
            std.error_2020 = mean(std.error_2020))

# Tidy 2021 data and join with 2020
### Choose filtered or unfiltered 2021 data
ed50_2021 <- fed50    # ed50 (unfiltered) or fed50 (filtered)
ed50_2021 <- ed50_2021 %>%
  mutate(ed50_2021 = estimate,
         std.error_2021 = std.error,
         nursery = tolower(nursery)) %>%
  select(nursery, geno, ed50_2021, std.error_2021)
alldf <- left_join(ed50_2021, ed50_2020, by = c("nursery", "geno")) %>%
  drop_na()

# # Plot raw ED50 values from 2021 vs. 2020
# plot1 <- ggplot(alldf, aes(x = ed50_2020, y = ed50_2021)) +
#   geom_point(aes(color = nursery, shape = nursery)) +
#   geom_errorbar(aes(xmin = ed50_2020 - std.error_2020, xmax = ed50_2020 + std.error_2020), lwd = 0.1) +
#   geom_errorbar(aes(ymin = ed50_2021 - std.error_2021, ymax = ed50_2021 + std.error_2021), lwd = 0.1) +
#   geom_text(aes(label = geno), size = 5) +
#   geom_smooth(aes(color = nursery, shape = nursery), method = "lm", se = FALSE) +
#   labs(x = "ED50 - 2020", y = "ED50 - 2021") +
#   coord_fixed(ratio = 1, xlim = c(34.5, 37.0), ylim = c(34.5, 37.0)) +
#   ggpubr::stat_cor(method = "pearson", label.y = 36.8, label.x = 34.5, size = 3)
#   #ggpubr::stat_cor(method = "spearman", label.y = 36.8, label.x = 34.5, size = 3)
# plot1
# 
# # Linear model for raw/unadjusted ED50 values
# mod <- lm(ed50_2021 ~ ed50_2020 + nursery, data = alldf)
# anova(mod)
```

# New analysis 2023
```{r}
# Combine data and convert to long format
alldf <- alldf %>%
  mutate(sum.std.error = std.error_2020 + std.error_2021)

longdf <- alldf %>%
  pivot_longer(cols = c(ed50_2021, ed50_2020, std.error_2020, std.error_2021), 
               names_to = "year", values_to = "value") %>%
  separate(year, into = c("var", "year"), sep = "_") %>%
  pivot_wider(names_from = var, values_from = value)


# Filter top genotypes based on quality of ED50 fitting
hist(alldf$sumse)
ggplot(alldf, aes(x = std.error_2020, y = std.error_2021)) + geom_point()
quantile(alldf$std.error_2020, 0.9)
quantile(alldf$std.error_2021, 0.9)
quantile(alldf$sum.std.error, 0.8)
top <- alldf %>%
  #arrange(sum.std.error) %>%
  #slice(1:50)
  #filter(std.error_2020 < 0.29 & std.error_2021 < 0.457); top
  filter(sum.std.error < 0.5858); top

#filtered2021 with sumse cutoff 0.677 (n=58) >> 0.303, 0.655
#filtered2021 with sumse cutoff 0.639 (top85%; n=56) >> 0.284, 0.642
#filtered2021 with sumse cutoff 0.586 (top80%; n = 52) >> 0.285, 0.619

toplongdf <- longdf %>%
  filter(geno %in% top$geno)

# Model nursery and year effects to remove from data
indf <- toplongdf
mod <- lm(ed50 ~ nursery:year, data = indf)
# Calculate grand mean ED50
gm <- mean(indf$ed50)
# Add residuals from nursery*year fitted values to the grand mean ED50
out <- augment(mod, indf) %>%
  mutate(ed50_adj = gm + .resid) %>%
  select(geno, nursery, year, ed50, ed50_adj) %>%
  pivot_wider(names_from = year, values_from = c(ed50, ed50_adj))

# Get ECDF for plotting
res2 <- out %>%
  mutate(diff = abs(ed50_adj_2021 - ed50_adj_2020))
dens <- density(res2$diff, adjust = 0.1)
dens <- tibble(x = dens$x, y = dens$y) %>%
  mutate(cd = cumsum(y)/sum(y))
# Get degree diffs for x% of cases from cumulative density
conf0.5 <- dens$x[which.min(abs(0.5 - dens$cd))]
conf0.9 <- dens$x[which.min(abs(0.9 - dens$cd))]

# Plot adjusted ED50s 2021 vs. 2020
left_join(out, alldf) %>%
ggplot(aes(x = ed50_adj_2020, y = ed50_adj_2021)) +
  geom_point(aes(color = sum.std.error)) +
  geom_ribbon(aes(ymin = ..x.. - conf0.5, ymax = ..x.. + conf0.5), alpha = 0.25) +
  geom_ribbon(aes(ymin = ..x.. - conf0.9, ymax = ..x.. + conf0.9), alpha = 0.25) +
  annotate("text", x = 35, y = 37, label = round(conf0.9, 3)) +
  annotate("text", x = 35, y = 36.8, label = round(conf0.5, 3)) +
  labs(x = "ED50 (°C) in Test 1 (2020)", y = "ED50 (°C) in Test 2 (2021)") +
  geom_abline(aes(slope = 1, intercept = 0), lty = 2, lwd = 0.25) +
  theme_custom() +
  #theme(legend.position = "none") +
  coord_fixed(expand = c(0.1,0.1))





```





####------
# everything below is older code from arond reef futures conference...
# Filter out ED50 measurements with high error (lower confidence in value)
```{r}
# Filter just ED50s with lower standard errors
#ggplot(alldf, aes(x = std.error_2020, y = std.error_2021)) + geom_point()

# Calculate sum of the ED50 standard errors for 2020 and 2021
alldf <- alldf %>% mutate(sum.std.error = (std.error_2021 + std.error_2020))
#hist(alldf$sum.std.error, breaks = 50)
boxplot(alldf$sum.std.error)

# Take highest-confidence 50 genotypes based on lowest combined standard error on ED50 measurements
highconf <- alldf %>%
  arrange(sum.std.error) %>%
  slice(1:50)

# Plot raw ED50 values from 2021 vs. 2020 for high-confidence genotypes
plot1 %+% highconf

# Linear model for raw ED50 values
mod <- lm(ed50_2021 ~ ed50_2020 + nursery, data = highconf)
anova(mod)
```

# Plot raw/unadjusted
```{r}
# Plot raw/unadjusted ED50s from 2021 to 2020

means <- highconf %>%
  pivot_longer(cols = c(ed50_2021, ed50_2020), names_to = "year") %>%
  group_by(nursery, year) %>%
  summarise(meanval = mean(value),
            sd = sd(value)) %>%
  pivot_wider(names_from = year, values_from = c(meanval, sd)) %>%
  select(nursery, ed50_2020 = meanval_ed50_2020, ed50_2021 = meanval_ed50_2021,
         sd_2020 = sd_ed50_2020, sd_2021 = sd_ed50_2021) %>%
  ungroup()
means


p1 <- highconf %>%
  ggplot(aes(x = ed50_2020, y = ed50_2021, color = nursery, fill = nursery)) +
  geom_point(size = 1, pch = 16, stroke = 0.25) +
  geom_abline(aes(slope = 1, intercept = 0), lty = 2, lwd = 0.25) +
  labs(x = "ED50 (°C) in Test 1 (2020)", y = "ED50 (°C) in Test 2 (2021)") +
  theme_custom() +
  theme(legend.position = "none") #+
  #coord_fixed(expand = FALSE)
ggsave(p1, filename = "output/p1.png", height = 75, width = 50, units = "mm")

p2 <- p1 +
  geom_point(data = means, size = 4, pch = 16) +
  geom_errorbar(data = means, aes(xmin = ed50_2020 - sd_2020, xmax = ed50_2020 + sd_2020), width = 0) +
  geom_errorbar(data = means, aes(ymin = ed50_2021 - sd_2021, ymax = ed50_2021 + sd_2021), width = 0)
ggsave(p2, filename = "output/p2.png", height = 75, width = 50, units = "mm")

int <- highconf %>%
  mutate(pred = ed50_2020 - 1 * ed50_2021) %>%
  group_by(nursery) %>%
  summarise(int = mean(pred))

p3 <- p2 +
  #geom_smooth(method = "lm", formula = y ~ x, se = FALSE) +
  geom_abline(aes(intercept = -int, slope = 1, color = nursery), data = int)
ggsave(p3, filename = "output/p3.png", height = 75, width = 50, units = "mm")
```

# Get adjusted ED50 values, removing nursery and year effects
```{r}
# Pivot to long form to model nursery:year differences and then subtract residuals
# Removes differences due to nursery and year to focus on genotype differences only
long <- highconf %>% drop_na() %>%
  select(nursery, geno, ed50_2021, ed50_2020) %>%
  pivot_longer(cols = c(ed50_2021, ed50_2020), names_to = "year", values_to = "ed50") 
mod <- lm(ed50 ~ nursery:year, data = long)
res <- augment(mod, long) %>%
  mutate(ed50_adj = mean(long$ed50) + .resid)

# Confirm that all nursery:year groups now have same mean value
means <- res %>%
  group_by(nursery, year) %>%
  summarise(meanvaladj = mean(ed50),
            sd = sd(ed50))

# Pivot to wide form to model 2021 vs. 2020
res2 <- res %>%
  select(nursery, geno, year, ed50_adj) %>%
  pivot_wider(names_from = year, values_from = ed50_adj)
```

# Compare ED50s from 2021 to 2020
```{r}
p4 <- res2 %>%
  ggplot(aes(x = ed50_2020, y = ed50_2021)) +
  geom_point(size = 1, pch = 1, stroke = 0.25) +
    geom_ribbon(aes(x = seq(34.8, 36.4, length.out = 50), 
                  ymin = ..x.. - filter(myvals, perc == 0.5) %>% pull(diff), 
                  ymax = ..x.. + filter(myvals, perc == 0.5) %>% pull(diff)), alpha = 0) +
  geom_ribbon(aes(x = seq(34.8, 36.4, length.out = 50),
                  ymin = ..x.. - filter(myvals, perc == 0.9) %>% pull(diff), 
                  ymax = ..x.. + filter(myvals, perc == 0.9) %>% pull(diff)), alpha = 0) +
  labs(x = "ED50 (°C) in Test 1 (2020)", y = "ED50 (°C) in Test 2 (2021)") +
  geom_abline(aes(slope = 1, intercept = 0), lty = 2, lwd = 0.25) +
  theme_custom() +
  theme(legend.position = "none") +
  coord_fixed(expand = FALSE)
ggsave(p4, filename = "output/p4.png", height = 75, width = 50, units = "mm")

p5 <- p4 + geom_segment(aes(y = ed50_2020, yend = ed50_2021, x = ed50_2020, xend = ed50_2020),
                  lwd = 0.2, color = "red")
ggsave(p5, filename = "output/p5.png", height = 75, width = 50, units = "mm")

# Model adjusted ED50ʻs from 2021 vs. 2020
## Linear model
mod.lm <- lm(ed50_2021 ~ ed50_2020, data = res2)
anova(mod.lm)
summary(mod.lm)
## Passing-Bablok, Deming, and quantile regressions
paba.reg <- mcreg(res2$ed50_2020, res2$ed50_2021, method.reg = "PaBa")
dem.reg <- mcreg(res2$ed50_2020, res2$ed50_2021, method.reg = "Deming")
mod.rq <- rq(ed50_2021 ~ ed50_2020, data = res2)

# Get ECDF for plotting
res2 <- res2 %>%
  mutate(diff = abs(ed50_2021 - ed50_2020))
dens <- density(res2$diff, adjust = 0.1)
dens <- tibble(x = dens$x, y = dens$y) %>%
  mutate(cd = cumsum(y)/sum(y))
# Get degree diffs for x% of cases from cumulative density
myvals <- tibble(perc = c(0.5, 0.9)) %>%
  mutate(diff = map_dbl(perc, ~ dens$x[which.min(abs(. - dens$cd))]))

# Plot ED50s with different regression lines
panelA <- res2 %>%
  ggplot(aes(x = ed50_2020, y = ed50_2021)) +
  geom_point(size = 1, pch = 1, stroke = 0.25) + #aes(color = abs(ed50_2020-ed50_2021) < 0.5)) +
  #geom_label(aes(label = geno)) +
  #geom_abline(aes(slope = coef(mod.lm)[2], intercept = coef(mod.lm)[1])) +
  #geom_abline(aes(slope = coef(mod.rq)[2], intercept = coef(mod.rq)[1])) +
  #geom_abline(aes(slope = paba.reg@para[2], intercept = paba.reg@para[1]), color = "blue") +
  #geom_abline(aes(slope = dem.reg@para[2], intercept = dem.reg@para[1]), color = "red") +
  geom_ribbon(aes(x = seq(34.8, 36.4, length.out = 50), 
                  ymin = ..x.. - filter(myvals, perc == 0.5) %>% pull(diff), 
                  ymax = ..x.. + filter(myvals, perc == 0.5) %>% pull(diff)), alpha = 0.2) +
  geom_ribbon(aes(x = seq(34.8, 36.4, length.out = 50),
                  ymin = ..x.. - filter(myvals, perc == 0.9) %>% pull(diff), 
                  ymax = ..x.. + filter(myvals, perc == 0.9) %>% pull(diff)), alpha = 0.2) +
  geom_abline(aes(slope = 1, intercept = 0), lty = 2, lwd = 0.25) +
  #ggpubr::stat_cor(method = "spearman", label.y = 36.7, label.x = 34.9, size = 3) +
  labs(x = "ED50 (°C) in Test 1 (2020)", y = "ED50 (°C) in Test 2 (2021)") +
  theme_custom() +
  theme(legend.position = "none") +
  coord_fixed(expand = FALSE); panelA
ggsave(panelA, filename = "output/panelA.png", height = 75, width = 50, units = "mm")

# Visualize ECDF
panelB <- ggplot(res2, aes(x = diff)) +
  #geom_segment(data = myvals, aes(y = perc, yend = perc, x = 0, xend = diff), lty = 2) +
  #geom_segment(data = myvals, aes(x = diff, xend = diff, y = 0, yend = perc), lty= 2) +
  geom_rect(data = myvals, aes(xmin = 0, xmax = diff, ymin = 0, ymax = perc), alpha = 0.2) +
  stat_ecdf(color = "red") +
  scale_x_continuous(breaks = seq(0,1.2,0.1), expand = c(0, 0), limits = c(0, 1.1)) +
  scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 0.9, 1), labels = scales::percent, expand = c(0, 0)) +
  labs(x = "|Test 1 - Test 2| ΔED50 (°C)", y = "Percent of cases") +
  theme_custom(); panelB 
ggsave(panelB, filename = "output/panelB.png", height = 75, width = 50, units = "mm")

# Visualize histogram of diffs
panelC <- res2 %>%
  mutate(diff = abs(ed50_2021 - ed50_2020)) %>%
  ggplot(aes(x = diff)) + 
  geom_histogram(aes(y = (..count..)/sum(..count..)), binwidth = 0.05, boundary = 0, closed = "left") +
  scale_x_continuous(breaks = seq(0,1.2,0.1), expand = c(0, 0), limits = c(0, 1.1)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.17)) +
  labs(x = "|Test 1 - Test 2| ΔED50 (°C)", y = "Percent of cases") +
  theme_custom(); panelC

col2 <- cowplot::plot_grid(panelB, panelC, ncol = 1, labels = c("B", "C"))
#cowplot::plot_grid(panelA, col2, ncol = 2, labels = c("A", ""))
panelB

fig1 <- cowplot::plot_grid(panelA, panelB, ncol = 2, labels = "AUTO")
fig1
ggsave(fig1, filename = "output/fig1.png", width = 89, height = 75, units = "mm")
```


# Estimate repeatability of ED50 for same genotype
```{r}
# Repeatability
library(rptR)
out <- rpt(ed50 ~ nursery * year  + (1|geno), data = long, grname = c("geno", "Overdispersion", "Fixed", "Residual"), nboot = 1000, parallel = TRUE, adjusted = TRUE)
out
plot(out)
summary(out)
```


# Repeatability of pairwise ranks
```{r}
# Get all pairwise differences in adjusted ED50 between high confidence genos in 2020 and 2021
genos <- res2$geno
diffs2020 <- outer(res2$ed50_2020, res2$ed50_2020, `-`)
dimnames(diffs2020) <- list(geno1 = genos, geno2 = genos)
diffs2021 <- outer(res2$ed50_2021, res2$ed50_2021, `-`)
dimnames(diffs2021) <- list(geno1 = genos, geno2 = genos)

diffs2021 <- reshape2::melt(diffs2021, value.name = "diff")
diffs2020 <- reshape2::melt(diffs2020, value.name = "diff")
alldiffs <- as_tibble(full_join(diffs2020, diffs2021, by = c("geno1", "geno2"), suffix = c(".20", ".21")))

# Plot pairwise ED50 differences in 2021 as a function of how much HIGHER one genet's 2020 ED50 was
alldiffs %>% 
  filter(diff.20 > 0) %>%       # Get all 2020 comparisons where genet 1 HIGHER than genet 2
  ggplot(aes(x = diff.20, y = diff.21)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE)

alldiffs %>% arrange(-diff.20)

diffs2 <- alldiffs %>% 
  filter(diff.20 > 0) %>%
  mutate(higher21 = diff.21 > 0)
ggplot(diffs2, aes(x = diff.20, y = higher21)) + geom_jitter()
mod <- glm(higher21 ~ diff.20, data = diffs2, family = "binomial")
anova(mod)

# Get probability that rank order is same given difference in 2020 ED50s
emm <- emmeans::emmeans(mod, specs = "diff.20", at = list(diff.20 = seq(0,2.0,0.01)), type = "response")

fig2 <- ggplot(data.frame(emm), aes(x = diff.20, y = prob)) +
  geom_line() +
  geom_ribbon(aes(ymin = asymp.LCL, ymax = asymp.UCL), alpha = 0.2) +
  labs(x = "Pairwise difference in ED50 (°C)\nin Test 1 (2020)",
       y = "Probability of same rank order\nin Test 2 (2021)") +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 2)) +
  theme_custom() +
  theme(text = element_text(size = 14)) +
  coord_cartesian(ylim = c(0.5, 1), expand = c(0, 0)); fig2

ggsave(fig2, filename = "output/fig2.png", width = 89, height = 89, units = "mm")

ggsave(fig2, filename = "output/f1.png", width = 50, height = 50, units = "mm")

```




```{r old_code, include = F, eval = F, echo = F}

#Repeatability coefficient
# Mean within-subject sample variance
res3 <- res2 %>% rowwise() %>% mutate(var = var(c(ed50_2021, ed50_2020)))
var_w <- mean(res3$var, na.rm = TRUE)
# Within-subject sample standard deviation
s_w <- sqrt(var_w)
# Coefficient of repeatability
rc95 <- 1.96 * sqrt(2) * s_w
rc95   # 95% of the time, repeat measurements will differ by less than rc     0.84
rc90 <- 1.645 * sqrt(2) * s_w
rc90

# statistical repeatability
probs <- tibble(
  p = seq(0.01, 0.99, 0.01),
  t = qt((1-seq(0.01,0.99,0.01))/2, lower.tail = F, df = Inf),
  y = t * sqrt(2) * s_w
)

ggplot(probs, aes(y = p, x = y)) +
  geom_line() +
  labs(y = "Percent of cases (genets)", x = "Test - retest difference in ED50 (°C)") +
  geom_vline(aes(xintercept = 0.95), lty = 2) +
  annotate("text", x = 0.8, y = 0.7, label = "Repeatability coefficient")

val <- qt((1-seq(0.01,0.99,0.01))/2, lower.tail = F, df = Inf) * sqrt(2) * s_w
plot(seq(0.01,0.99,0.01), val)
pt(seq(0.01,0.99,0.01), df = Inf) * sqrt(2) * s_w
plot(seq(0.01,0.99,0.01), tt)



```

